Methods

### 2019-01-23 Methods.Rmd
testing bits OISST/MUR

SACTN_daily_temps_indexsplit <- SACTN_daily_temps %>% 
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>% 
  dplyr::rename(insitu_temp = temp)
# save(SACTN_daily_temps_indexsplit, file = "Data/SACTN_daily_temps_indexsplit.RData")
```

@@

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(2015, 2016))
```

```{r}
ggplot(data = SACTN_3yr , aes(x = date, y = insitu_temp)) +
  geom_hline(aes(yintercept = mean(insitu_temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 2) +
  theme_bw()
```

@@

Here i am suppose to overlap the MUR data with the insitu collected data but the insitu collected data is from 199-2000
- find other overlapping more recent time with the in situ data?
-

@@

save(MUR_SST, file = "Data/MUR_SST.RData")
```

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/MUR_SST.RData")
```

@@

insitu_MUR <- match_func(df = MUR_SST)
```

@@

```{r}
ggplot(data = OISST_match, aes(x = date, y = temp)) +
  geom_line() +
  facet_wrap(~combi)
ggsave(plot = OISST_match, filename = "Figures/combined_OISST_match")
```

@@

save(OISST_sites, file = "Data/OISST_sites.RData")
```

```{r}
# load("~/Documents/MastersProject/Data/combined_OISST_sites.RData")
```

>>>>

SACTN_daily_temps_indexsplit <- SACTN_daily_temps %>% 
  separate(index, into = c("site", "src"), sep = "/", remove = FALSE) %>% 
  dplyr::rename(insitu_temp = temp)

# save(SACTN_daily_temps_indexsplit, file = "Data/SACTN_daily_temps_indexsplit.RData")
```

This code is testing out the wavelet analyses for the in situ temperature data

```{r}
SACTN_wavelet <- SACTN_daily_temps_indexsplit %>% 
  filter(year(date) %in% seq(2015, 2016))

SACTN_wavelet.d <- SACTN_wavelet %>% 
  dplyr::group_by(site, date) %>% 
  dplyr::summarise(temp = mean(insitu_temp, na.rm = TRUE)) %>% 
  dplyr::mutate(no = seq(1:n())) %>%
  dplyr::ungroup() %>% 
  dplyr::select(site, no, temp, date)

ggplot(data = SACTN_wavelet, aes(x = date, y = insitu_temp)) +
  geom_hline(aes(yintercept = mean(insitu_temp)), colour = "salmon") +
  geom_line() +
  facet_wrap(~ site, nrow = 4) +
  theme_bw()

auto.arima(dplyr::filter(SACTN_wavelet, site == "Port Nolloth")[, "insitu_temp"], max.p = 3, max.q = 3, stationary = FALSE, 
           seasonal = FALSE)

PN <- SACTN_wavelet.d %>% 
  dplyr::filter(site == "Port Nolloth") %>% 
  dplyr::select(temp, -date, -site) %>% 
  dplyr::mutate(no = seq(1:n())) %>% 
  dplyr::select(no, temp)
```

@@

SACTN_3yr <- SACTN_split %>% 
  filter(year(date) %in% seq(2015, 2016)) %>% 
  drop_na() # Removing NA values within the dataset
```

@@

@@

# save(MUR_SST, file = "Data/MUR_SST.RData")
```

```{r}
load("~/Documents/Masters_2019/MastersProject/Data/MUR_SST.RData")

MUR_SST <- MUR_SST %>% 
  drop_na()
```

@@

insitu_MUR <- match_func(df = MUR_SST) %>%
  drop_na()
```

@@

```{r}
ggplot(data = OISST_match, aes(x = date, y = temp_OISST)) +
  geom_line() +
  facet_wrap(~combi)
ggsave(plot = OISST_match, filename = "Figures/combined_OISST_match")
```

@@

# save(OISST_sites, file = "Data/OISST_sites.RData")
```

```{r}
load("~/Documents/MastersProject/Data/OISST_sites.RData")

OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST)
```
